---
title: "Capstone Project Quizz 1"
author: "Erick Yegon"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
setwd("C:/Users/Erick Yegon/Dropbox/My PC (DESKTOP-1I4SCDT)/Desktop/Capstone/final")
```

# Question 1
# The en_US.blogs.txt  file is how many megabytes?

```{r}
file.info("en_US/en_US.blogs.txt")$size / 1024^2
```
# Question 2
# The en_US.twitter.txt has how many lines of text?

```{r}
blogs <- readLines("en_US/en_US.blogs.txt")
news <- readLines("en_US/en_US.news.txt")
twitter <- readLines("en_US/en_US.twitter.txt")
length(twitter)
```

# Question 3
# What is the length of the longest line seen in any of the three en_US data sets?

```{r}
max(nchar(blogs))
max(nchar(news))
max(nchar(twitter))
```


# Question 4
# In the en_US twitter data set, if you divide the number of lines where the word "love" 
# (all lowercase) occurs by the number of lines the word "hate" 
#(all lowercase) occurs, about what do you get?

```{r}
love_count <- sum(grepl("love", twitter))
hate_count <- sum(grepl("hate", twitter))
love_count / hate_count

```

# Question 5
# The one tweet in the en_US twitter data set that matches the word "biostats" says what?

```{r}
biostats <- grep("biostats", twitter)
twitter[biostats]
```

# Question 6
# How many tweets have the exact characters 
#"A computer once beat me at chess, but it was no match for me at kickboxing". 
#(I.e. the line matches those characters exactly.)
```{r}

sum(grepl("A computer once beat me at chess, but it was no match for me at kickboxing", twitter))

```

